\documentclass[11pt,letterpaper]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES & SETUP
%----------------------------------------------------------------------------------------

\usepackage[left=0.5 in,top=0.5in,right=0.5 in,bottom=0.5in]{geometry} % Document margins
\usepackage[parfill]{parskip} % Remove paragraph indentation
\usepackage{array} % Required for boldface (\bf and \bfseries) tabular columns
\usepackage{enumitem}
\usepackage{fontawesome}
\usepackage{hyperref}
% \hypersetup{
%     colorlinks=true,
%     linkcolor=blue,
%     filecolor=magenta,      
%     urlcolor=blue,
% }

\pagestyle{empty} % Suppress page numbers

\setlist[itemize,1]{label=\tiny$\bullet$}

\begin{document}

\centerline{\Huge\bf Ethan Thomas} 
\vspace{1pt}
\centerline{\small{\faMobile \space +1 (863) 325 5360 $|$ \faAt \space ethan@smaze.net $|$ \href{https://www.linkedin.com/in/ethanmt/}{\faLinkedinSquare \space ethanmt} $|$ \href{https://github.com/ethmth}{\faGithub \space ethmth} $|$ \href{https://www.ethanmt.com}{\faGlobe \space www.ethanmt.com} $|$ \faMapMarker \space Winter Haven, FL}}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\vspace{6pt}
\textsc{\large{Education}} 
\vspace{4pt}
\hrule
\begin{list}{}{\setlength{\leftmargin}{1em}\setlength{\rightmargin}{2pt}}
    \item
                
            \textbf{Columbia University} \hfill  {New York, NY}
            \vspace{2pt} \newline
            \small{\textit{B.S. in Computer Science \quad \textbf{GPA: 4.157/4.0}}} \hfill {\small{\textit{Sep. 2022 \textendash \space Oct. 2024}}}
            \vspace{0pt}
            \begin{itemize}[itemsep=-5pt, topsep=-2pt]
                \item \small{\textit{Organizations: Application Development Initiative, Tau Beta Pi, Columbia Space Initiative}}
            \end{itemize}
            %   Coursework: Artificial Intelligence, Data Structures, Algorithms, Databases, Networks, Operating Systems, Security
\end{list}

%----------------------------------------------------------------------------------------
% EXPERIENCE 
%----------------------------------------------------------------------------------------

\vspace{4pt}
\textsc{\large{Experience}} 
\vspace{4pt}
\hrule
\begin{list}{}{\setlength{\leftmargin}{1em}\setlength{\rightmargin}{2pt}}
  
    \item
        \normalsize{\textbf{Florida Atlantic University}} \hfill Boca Raton, FL
          \vspace{2pt} \newline
          \small{\textit{Engineering Research Intern}} \hfill \small{\textit{Jun. 2023 \textendash \space Aug. 2023}}
          \vspace{0pt}
          \begin{itemize}[itemsep=-5pt, topsep=-2pt]
              \item Secured funding from \textbf{NSF's Engineering Research Center for Smart Streetscapes (CS3)}.
              \item Conducted analysis of scooter data to classify riding surfaces for enhanced safety and asset management.
              \item Developed a \textbf{Raspberry Pi}-based \textbf{data collection system} with IMU, GPS, and speed sensors.
              \item Automated tasks using Systemd services, \textbf{bash scripts}, and \textbf{Python} IPC libraries.
              \item \textbf{Trained PyTorch and scikit-learn models}, achieving \textbf{90\% classification accuracy}.
              \item Won ``\textbf{Most Outstanding Presentation}'' award for project results.
          \end{itemize}
          \vspace{4pt}

    \item
        \normalsize{\textbf{Puberry Inc.}} \hfill New York, NY
          \vspace{2pt} \newline
          \small{\textit{Software Engineering Intern}} \hfill \small{\textit{Feb. 2023 \textendash \space Jun. 2023}}
          \vspace{0pt}
          \begin{itemize}[itemsep=-4pt, topsep=-2pt]
              \item Developed interactive quizzes and a progress-tracking calendar for a \textbf{cross-platform puberty education app}.
              \item Contributed to the \textbf{Flutter front-end}, implementing responsive design and seamless user interactions.
              \item Connected the app to \textbf{Google Firebase} for secure data storage and user authentication.
              \item Contributed to the demo sprint, enabling a successful pilot test with students and teachers.
              \item Helped Puberry \textbf{improve health test scores by 61\%}.
          \end{itemize}
\end{list}

%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------

\vspace{4pt}
\textsc{\large{Projects}} 
\vspace{4pt}
\hrule
\begin{list}{}{\setlength{\leftmargin}{1em}\setlength{\rightmargin}{2pt}}
  
    \item
        \small{\textbf{DevFest Hackathon Website}} $|$ \small{\textit{Next.js, React, UI Design, Project Management}} \hfill \small{\textit{\href{https://2024.devfestcu.com/}{2024.devfestcu.com}}}
          \begin{itemize}[itemsep=-5pt, topsep=-2pt]
              \item \textbf{Led a team} of five engineers to develop Columbia University's \textbf{DevFest 2024 website}.
              \item Designed a \textbf{Next.js} and \textbf{React} site styled as a comic book with interactive ``page turning'' features.
              \item Improved event registration \textbf{by 100+ participants} compared to 2023 through clear, accessible information design.
          \end{itemize}
          \vspace{4pt}

    \item
        \small{\textbf{Pitch Wizard}} $|$ \small{\textit{Python, Flask, HTML/CSS, JavaScript, jQuery, Docker, UI/UX Design}} \hfill \small{\textit{\href{https://pitchwizard.lol/}{pitchwizard.lol}}}
          \begin{itemize}[itemsep=-5pt, topsep=-2pt]
              \item Developed a web app to \textbf{teach users how to identify baseball pitches}, like fastballs and curveballs.
              \item Created an \textbf{interactive lesson and quiz} using \textbf{Flask} for the back-end and Flask sessions for progress tracking.
              \item Designed and implemented the front-end UI with \textbf{HTML/CSS}, \textbf{JavaScript}, and \textbf{jQuery}.
            %   \item Achieved user \textbf{success rates of 85\%+} in identifying pitch types after completing the lessons.
          \end{itemize}
          \vspace{4pt}
    
    \item
        \small{\textbf{OpenAir-VPN}} $|$ \small{\textit{Linux, Bash, Shell Scripting, Networking, CLI}} \hfill \small{\textit{}}
          \begin{itemize}[itemsep=-5pt, topsep=-2pt]
              \item Developed a \textbf{Linux command-line interface (CLI)} to manage Wireguard and OpenVPN connections.
              \item Implemented an iptables-based killswitch, startup/shutdown integration with Systemd, and optional LAN access.
              \item Published the project as \textbf{open-source} under the MIT license, prioritizing ease of use and community contributions.
          \end{itemize}
          \vspace{4pt}
    
    % \item
    %       \textbf{Baseball Analytics Dashboard} $|$ \small{\textit{React, R, RESTful, API}} \hfill \small{\textit{}}
    %       \begin{itemize}[itemsep=-5pt, topsep=-2pt]
    %           \item Built a \textbf{React-based web interface} for visualizing pitch data as part of Georgetown Baseball Analytics.
    %           \item Integrated with an \textbf{R Plumber REST API} to display pitch trajectories and strike zone grids.
    %           \item Provided coaches and players with an interactive tool to better understand pitching performance.
    %       \end{itemize}
\end{list}


%----------------------------------------------------------------------------------------
% SKILLS
%----------------------------------------------------------------------------------------

\vspace{4pt}
\textsc{\large{Skills}} 
\vspace{4pt}
\hrule
\begin{list}{}{\setlength{\leftmargin}{1em}\setlength{\rightmargin}{2pt}}
  
    \item
          \small{\textbf{Programming Languages:} Python, C, C++, SQL, JavaScript, TypeScript, Java, OCaml}
          \vspace{2pt} \newline
          \small{\textbf{Technical Skills:} Git, Linux, Docker, Bash, LaTeX, HTML, CSS, Virtual Machines, UX/UI Design}
          \vspace{2pt} \newline
          \small{\textbf{Libraries \& Frameworks:} React, Next.js, Node.js, Flutter, PyTorch, Selenium, Flask, Godot, PostgreSQL}
          \vspace{2pt} \newline
          \small{\textbf{Soft Skills:} Problem Solving, Communication, Prototying, Creative Thinking, Teamwork, Leadership}
          \vspace{0pt}
\end{list}

\end{document}

