\documentclass[11pt,letterpaper]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES & SETUP
%----------------------------------------------------------------------------------------


\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\usepackage[parfill]{parskip} % Remove paragraph indentation
\usepackage{array} % Required for boldface (\bf and \bfseries) tabular columns

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\pagestyle{empty} % Suppress page numbers

%----------------------------------------------------------------------------------------
%	HEADINGS COMMANDS: Commands for printing name and address
%----------------------------------------------------------------------------------------

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\begin{document}
% NAME
\begingroup
    %\hfil{\MakeUppercase{\LARGE\bf Ethan M Thomas}}
    \centerline{\MakeUppercase{\LARGE\bf Ethan M Thomas}}
    % \medskip\break
    \medskip
    % \break
\endgroup

% ADDRESS LINE 1
\begingroup
\centerline{+1(863) 325-5360 • ethan@smaze.net}
\endgroup
\par

% ADDRESS LINE 2
\begingroup
\centerline{\href{www.ethanmt.com}{www.ethanmt.com} • \href{https://www.linkedin.com/in/ethanmt/}{linkedin.com/in/ethanmt} • \href{https://github.com/ethmth}{github.com/ethmth}}
\endgroup
\par

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\medskip
\MakeUppercase{{\bf Objective}} % Section title
\medskip
\hrule % Horizontal line
\begin{list}{}{\setlength{\leftmargin}{0em}}
\item 
    %{Software Engineer with 2+ years of experience in XXX, seeking full-time XXX roles.}
    {Student passionate about Computer Science, specifically Linux, automation using Bash and Python, and Front-end Development. Seeking a Summer 2023 Software Engineering internship.}
\end{list}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\medskip
\MakeUppercase{{\bf Education}} % Section title
\medskip
\hrule % Horizontal line
\begin{list}{}{\setlength{\leftmargin}{0em}}
\item 
{\bf Bachelor of Computer Science (B.S.)}, Columbia University (SEAS) \hfill  {Class of 2025}\\
Relevant Coursework: Data Structures, Advanced Programming, Linear Algebra, Discrete Math \hfill {GPA: 4.0}
%\item 
\\
Member of Columbia Space Initiative - 2023 NASA Micro-g NExT Competition Team Member \\ 
Member of the Application Development Initiative - DevFest (Hackathon) Organizing Committee
\end{list}


%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------

\medskip
\MakeUppercase{{\bf Skills}} % Section title
\medskip
\hrule % Horizontal line
\begin{list}{}{\setlength{\leftmargin}{0em}}
\item 
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Programming Languages & Java, C++, C, Python, Javascript, Typescript, R \\
    Libraries & Selenium, Flask API, Beautiful Soup, React, NextJS, RPlumber \\ 
    Technical Skills & Linux, Docker, Bash, Latex, HTML, CSS, Git, CAD (Solidworks) \\
    Soft Skills & Communication, Leadership, Organization\\
    \end{tabular}
\end{list}


%----------------------------------------------------------------------------------------
% EXPERIENCE 
%----------------------------------------------------------------------------------------


\medskip
\MakeUppercase{{\bf Experience}} % Section title
\medskip
\hrule % Horizontal line
\begin{list}{}{\setlength{\leftmargin}{0em}}
\item 
\textbf{Front-End Software Engineer (Georgetown University Club)} \hfill Sep 2021 - May 2022\\
Georgetown University Baseball Analytics \hfill \textit{Washington, DC}
 \begin{itemize}
    \itemsep -3pt {} 
    \item Developed proof-of-concept web UI that allowed coaches and players to visualize catcher framing data using ReactJS and R. \
        \href{https://gu-baseball.herokuapp.com/catcher_framing}{gu-baseball.herokuapp.com/catcher\_framing} (Dummy data; API loading times may vary).
    \item Worked with R Data Analysts to convert their projects into APIs using the R Plumber Library.
 \end{itemize}

 \item
 \textbf{Web Developer/Web Designer (Volunteer)} \hfill July 2019 - May 2021\\
 Winter Haven Optimist Club \hfill \textit{Winter Haven, FL}
  \begin{itemize}
     \itemsep -3pt {} 
     \item Developed and designed a new website for an annual Christmas 5k/10k fundraiser using HTML/CSS.
     \item Achieved X\% growth in traffic to their site with my design.
  \end{itemize}
\end{list}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\medskip
\MakeUppercase{{\bf Projects}} % Section title
\medskip
\hrule % Horizontal line
\begin{list}{}{\setlength{\leftmargin}{0em}}
\item % needed for spacing
\vspace{-1.25em}
\item \textbf{Hiring Search Tool.} {Built a tool to search for Hiring Managers and Recruiters by using ReactJS, NodeJS, Firebase and boolean queries. Over 25000 people have used it so far, with 5000+ queries being saved and shared, and search results even better than LinkedIn! \href{https://hiring-search.careerflow.ai/}{(Try it here)}}
\item \textbf{Short Project Title.} {Build a project that does something and had quantified success using A, B, and C. This project's description spans two lines and also won an award.}
\item \textbf{Short Project Title.} {Build a project that does something and had quantified success using A, B, and C. This project's description spans two lines and also won an award.}
\end{list}

%----------------------------------------------------------------------------------------

\medskip
\MakeUppercase{{\bf Extra-Curricular Activities}} % Section title
\medskip
\hrule % Horizontal line
\begin{list}{}{\setlength{\leftmargin}{0em}}
\item
\begin{itemize}
    \item 	Actively write \href{https://www.faangpath.com/blog/}{blog posts} and social media posts (\href{https://www.tiktok.com/@faangpath}{TikTok}, \href{https://www.instagram.com/faangpath/?hl=en}{Instagram}) viewed by over 20K+ job seekers per week to help people with best practices to land their dream jobs. 
    \item	Sample bullet point.
\end{itemize}
\end{list}


%----------------------------------------------------------------------------------------

\medskip
\MakeUppercase{{\bf Leadership}} % Section title
\medskip
\hrule % Horizontal line
\begin{list}{}{\setlength{\leftmargin}{0em}}
\item
\begin{itemize}
    \item Admin for the \href{https://discord.com/invite/WWbjEaZ}{FAANGPath Discord community} with over 6000+ job seekers and industry mentors. Actively involved in facilitating online events, career conversations, and more alongside other admins and a team of volunteer moderators! 
\end{itemize}
\end{list}


\end{document}

